Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-21 summary.Rmd
intermediate commit to move some files

ggplot(densities.df) + 
  geom_density(aes(x = inner.prods, colour = factor(n))) + 
  labs(x = 'between cluster inner products',
       colour = 'n') + 
  scale_colour_brewer(palette = 'Set1')
```

@@

z.hat <- cluster.pabm(A, K)
A.star <- A[order(z.hat), order(z.hat)]

@@

plot.A <- function(A, labels) {
  # https://www.r-graph-gallery.com/79-levelplot-with-ggplot2.html
  A[order(labels), order(labels)] %>% 
    tibble::as_tibble() %>% 
    tibble::rowid_to_column(var = 'X') %>% 
    tidyr::gather(key = 'Y', value = 'Z', -1) %>% 
    dplyr::mutate(Y = rev(as.numeric(gsub('V', '', Y)))) %>% 
    ggplot() + 
    geom_tile(aes(x = X, y = Y, fill = Z)) + 
    coord_fixed() + 
    labs(x = NULL, y = NULL) + 
    theme_void() + 
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) + 
    scale_x_continuous(expand = c(0, 0)) + 
    scale_y_continuous(expand = c(0, 0)) + 
    scale_fill_gradient(low = 'red', high = 'yellow')
}
```

```{r butterfly, fig.height = 2, fig.width = 2, fig.cap = 'Adjacency matrix of the Leeds Butterfly dataset after sorting by the clustering outputted by Algorithm 2.', cache = TRUE}
plot.A(A.star)
```

@@

```{r, cache = TRUE}
zhat.bmp <- cluster.pabm(A.bmp, 2, use.all = TRUE, normalize = TRUE)
bmp.acc <- mean(zhat.bmp == z.bmp)

zhat.pb <- cluster.pabm(A.pb, 2, use.all = TRUE, normalize = TRUE, 
                        p = 2, q = 0)
pb.acc <- mean(zhat.pb == z.pb)

@@

```{r mp, cache = TRUE, fig.width = 8, fig.height = 2, fig.cap = 'Adjacency matrices of (from left to right) the British MPs, Political Blogs, and DBLP networks after sorting by the clustering outputted by Algorithm 2.', fig.dpi = 25}
gridExtra::grid.arrange(plot.A(A.bmp, zhat.bmp),
                        plot.A(A.pb, zhat.pb),
                        plot.A(A.dblp, zhat.dblp),
                        ncol = 3)

```

>>>>

ggplot(densities.df) + 
  geom_density(aes(x = inner.prods * sqrt(n), colour = factor(n))) + 
  labs(x = 'between cluster inner products',
       colour = 'n') + 
  scale_colour_brewer(palette = 'Set1')
```

@@

z.hat <- cluster.pabm(A, K)

@@

plot.A <- function(A, labels, max.size = 500) {
  # https://www.r-graph-gallery.com/79-levelplot-with-ggplot2.html
  A <- A[order(labels), order(labels)]
  n <- nrow(A)
  if (n > max.size) {
    ind <- sort(sample(seq(n), max.size))
    A <- A[ind, ind]
  }
  A %>% 
    tibble::as_tibble() %>% 
    tibble::rowid_to_column(var = 'X') %>% 
    tidyr::gather(key = 'Y', value = 'Z', -1) %>% 
    dplyr::mutate(Y = rev(as.numeric(gsub('V', '', Y)))) %>% 
    ggplot() + 
    geom_tile(aes(x = X, y = Y, fill = Z)) + 
    coord_fixed() + 
    labs(x = NULL, y = NULL) + 
    theme_void() + 
    theme(legend.position = 'none',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank()) + 
    scale_x_continuous(expand = c(0, 0)) + 
    scale_y_continuous(expand = c(0, 0)) + 
    scale_fill_gradient(low = 'red', high = 'yellow')
}
```

```{r butterfly, fig.height = 2, fig.width = 2, fig.cap = 'Adjacency matrix of the Leeds Butterfly dataset after sorting by the clustering outputted by Algorithm 2.', cache = FALSE}
plot.A(A, z.hat)
```

@@

```{r, cache = TRUE}
zhat.bmp <- cluster.pabm(A.bmp, 2, use.all = TRUE, normalize = FALSE)
bmp.acc <- mean(zhat.bmp == z.bmp)

zhat.pb <- cluster.pabm(A.pb, 2, use.all = TRUE, normalize = FALSE, 
                        p = 2, q = 0, d.eigenmap = 2)
pb.acc <- mean(zhat.pb == z.pb)

@@

```{r mp, cache = TRUE, fig.width = 8, fig.height = 2, fig.cap = 'Adjacency matrices of (from left to right) the British MPs, Political Blogs, and DBLP networks after sorting by the clustering outputted by Algorithm 2.', fig.dpi = 10}
gridExtra::grid.arrange(plot.A(A.bmp, zhat.bmp),
                        plot.A(A.pb, zhat.pb),
                        plot.A(A.dblp, zhat.dblp),
                        ncol = 3)
```
